Text as Policy: \\ Measuring Policy Similarity through Bill Text Reuse

### 2016-07-21 manuscript/main.tex
updates to paper

In the previous two validity tests, we focused mainly on the policy domain aspect of policy similarity, rather than ideological similarity. In the third and final validity test we ask whether we observe a greater volume of text reuse between bills introduced by legislators who are ideologically similar. For calculating ideological distance, we rely on latent ideology scores measured by \citep{shor2011}. The data set contains scores for 20,738 legislators from 50 state legislatures. The \texttt{openstates} API, which we can match to our bills data, contains data and identifiers on $12,000$ legislators. Of these, we where able to uniquely match about $8,000$ legislators to their records in the ideal point data. This allowed us to obtain ideal points for the sponsors of $58\%$ of bills and 1,745,336 ($37\%$) pairs of bills.[{\bf Frido, should these numbers be updated? They seem to be disconnected from the numbers below.}] In order to assess the validity of text reuse as a measure of substantive policy overlap, we expect the quality of the alignments to be inversely correlated to the distance between the bills sponsors' ideal points. The ideal points are located on a common scale across all states, the distance between sponsors from different states is therefore meaningful.

@@

\begin{figure}[ht!]
    \centering
    \includegraphics[width=0.8\textwidth]{figures/ideology_quantile_plot.png}
    \caption{Hexbin plot of alignment score and ideological distance of all 50 million bill dyads. The lines indicate different quantiles of the distribution of alignment scores conditional on the ideological distance. See Figure \ref{fig:quantile_regression} for exact quantiles, coefficients and uncertainty.}
    \label{fig:ideology_quantile_plot}
\end{figure}

>>>>

In the previous two validity tests, we focused mainly on the policy domain
aspect of policy similarity, rather than ideological similarity. In the third
and final validity test we ask whether we observe a greater volume of text reuse
between bills introduced by legislators who are ideologically similar. For
calculating ideological distance, we rely on latent ideology scores measured by
\citep{shor2011}. The data set contains scores for 20,738 legislators from 50
state legislatures. The \texttt{openstates} API, which we can match to our bills
data, contains data and identifiers on $12,000$ legislators. Of these, we where
able to uniquely match about $8,000$ legislators to their records in the ideal
point data. This allowed us to obtain ideal points for the sponsors of $58\%$ of
bills and $48*10^6$ ($38\%$) pairs of bills. In order to assess the validity of text reuse as a measure of substantive policy overlap, we expect the quality of the alignments to be inversely correlated to the distance between the bills sponsors' ideal points. The ideal points are located on a common scale across all states, the distance between sponsors from different states is therefore meaningful.

@@
